Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-07-04 paper/manuscript.Rmd
Split funding from awknoledgements

>>>>

Fieldwork was supported by grants PICT 08–12504 and 0851. 
EFC acknowledges the support from the University of Canterbury Doctoral Scholarship and a New Zealand International Doctoral Research Scholarship administered by New Zealand Education. 
DBS and JMT acknowledge the support of Rutherford Discovery Fellowships (RDF-13-UOC-003 and RDF-UOC-1002) and the Marsden Fund Council (UOC-1705), administered by the Royal Society of New Zealand Te Apārangi.
